Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-23 automatica/paper.tex
fixes

\note{[shouldn't this be a bullet point too?]}
The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
thus we must account for the corresponding errors.  
\note{rephrase next - main clause has no verb:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
We \note{guarantee [?]} that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.

>>>>

\note{[shouldn't this be a bullet point too?] It can't be in the previous list though because ti isn't an error introduced by the nature of digital control and that we need to model, it is an error introduced *by* our modelling}
The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
thus we must account for the corresponding errors.  
Specifically, we must account for the error introduced by our model using finite-precision arithmetic for the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities. 
We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
